Consistent Polyhedral Surrogates via Embedding

### 2019-06-02 notes/raf-lovasz.tex
lovasz comment
Changed refs for the Bach book

Given set function $f$ with Lov\'asz extension $F$, \citet{yu2018lovasz} define the \emph{Lov\'asz hinge} as the loss $L^f:\reals^k\times\Y\to\reals$ given by
\begin{equation}
  \label{eq:lovasz-hinge}
  L^f(u,S) =
  \begin{cases}
    F\bigl((\ones - u \odot \chi_S)_+\bigr) & \text{if $f$ is increasing}
    \\
    \bigl(F(\ones - u \odot \chi_S)\bigr)_+ & \text{otherwise}
  \end{cases}~,
\end{equation}
where $v (u \odot y)_i = u_iy_i$ is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.

@@

  To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
  It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 19) in \citet{bach2013learning}.
  We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
  For any $A\subseteq N$ and permutation $\pi$, let
  \begin{equation}
    \label{eq:poly-pi}
    P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
  \end{equation}
  That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.

  Condition (i) follows immediately: for any $u\in[-1,1]^k$, let $A = \{i:u_i\geq 0\}$, and $\pi$ be any permutation ordering the elements of $u \odot \chi_A$.
  For condition (ii), note that for any $u\in P^A_\pi$, as $u\odot \chi_A \in P_\pi$ we may write
  \begin{equation}
    \label{eq:udot-conv}
    u \odot \chi_A = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} + u_{\pi_k} (\chi_A)_{\pi_k} \ones
    % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
    ~,
  \end{equation}
  which is a convex combination (again, see \citet[pg.\ 20]{bach2013learning}).
  We simply apply the involution $\odot\chi_A$ again, to obtain
  \begin{equation}
    \label{eq:udot-conv}
    u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
    % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
    ~,
  \end{equation}
  and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.

@@

\begin{theorem}
  Let $f$ be submodular, normalized, and increasing.
  Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
\end{theorem}
\begin{proof}
  If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
  We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
  (Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
  Calibration and consistency then follow.
  \raft{Too informal; should flesh out}

>>>>

Given set function $f$ with Lov\'asz extension $F$, \citet{yu2018lovasz} define the \emph{Lov\'asz hinge} as the loss $L^f:\reals^k\times\Y\to\reals$ given by
\begin{equation}
  \label{eq:lovasz-hinge}
  L^f(u,S) =
  \begin{cases}
    F\bigl((\ones - u \odot \chi_S)_+\bigr) & \text{if $f$ is increasing}
    \\
    \bigl(F(\ones - u \odot \chi_S)\bigr)_+ & \text{otherwise}
  \end{cases}~,
\end{equation}
where $v (u \odot y)_i = u_iy_i$ \jessiet{What is $v$ here?} is the Hadamard (element-wise) product and $((u)_+)_i = \max(u_i,0)$.
In what follows, we focus on the increasing case, which is the most natural: when you make an additional error, your loss cannot decrease.

@@

  To begin, let us recall the polyhedra on which the Lov\'asz extension is linear; for any permutation $\pi$, define $P_\pi = \{u\in\reals^k : u_{\pi_1} \geq \cdots \geq u_{\pi_k}\}$.
  It is clear from the definition that $F$ is linear on $P_\pi$; see also Equation 3.1, and ``Linear interpolation on simplices'' (pg.\ 167) in \citet{bach2013learning}.
  We will use these polyhedra to identify the regions where $L(\cdot,S)$ is linear simultaneously for all outcomes $S\in\Y$.
  For any $A\subseteq N$ and permutation $\pi$, let
  \begin{equation}
    \label{eq:poly-pi}
    P^A_\pi = \{u\in[-1,1]^k : u \odot \chi_A \in P_\pi \cap \reals^k_+\}~.
  \end{equation}
  That is, $P^A_\pi$ contains all points $u$ such that $u \odot \chi_A$ is nonnegative (meaning $\sgn(u)$ matches $\chi_A$, breaking ties at $0$ favorably) and such that the coordinates of $u \odot \chi_A$ are in increasing order according to $\pi$.

  Condition (i) follows immediately: for any $u\in[-1,1]^k$, let $A = \{i:u_i\geq 0\}$, and $\pi$ be any permutation ordering the elements of $u \odot \chi_A$.
  For condition (ii), note that for any $u\in P^A_\pi$, as $u\odot \chi_A \in P_\pi$ we may write
  \begin{equation}
    \label{eq:udot-conv}
    u \odot \chi_A = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}} + u_{\pi_k} (\chi_A)_{\pi_k} \ones
    % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
    ~,
  \end{equation}
  which is a convex combination (again, see \citet[pg.\ 167]{bach2013learning}).
  We simply apply the involution $\odot\chi_A$ again, to obtain
  \begin{equation}
    \label{eq:udot-conv}
    u = \sum_{i=1}^{k-1} \left( u_{\pi_i} (\chi_A)_{\pi_i} - u_{\pi_{i+1}} (\chi_A)_{\pi_{i+1}} \right) \ones_{\{\pi_1,\ldots,\pi_i\}}\odot \chi_A + u_{\pi_k} (\chi_A)_{\pi_k} \chi_A
    % + (1-u_{\pi_1}(\chi_A)_{\pi_1} \cdot 0
    ~,
  \end{equation}
  and condition (ii) follows as $\ones_B \cdot \chi_A \in \U$ for all sets $B\subseteq N$.

@@

\begin{theorem}
  Let $f$ be submodular, normalized, and increasing.
  Then $(L^f,\sgn)$ is consistent if and only if $f$ is modular.
\end{theorem}
\begin{proof}
  If $f$ is modular, then $F$ is linear, and $L^f(\cdot;p)$ is linear on $[-1,1]^k$.
  We conclude that $L^f(\cdot;p)$ is minimized at a vertex of the hypercube, meaning $L^f$ embeds $2\ell^f$.
  (Equivalently, there is always an optimal report $(A,\emptyset)\in\hat\R$ for $\hat\ell^f$.)
  Calibration and consistency then follow.
  \raft{Too informal; should flesh out---in particular, is there is easy way to see that $\sgn$ works using our construction?}
